Consumption and resistance across states

### 2017-02-07 states/resistance/report2/state-report.Rmd
state report 2 done

  p = plot_dat %>%
    filter(bug==row$bug, consumption_drug==row$consumption_drug) %>%
    ggplot(aes_string(row$explanatory, 'percent_susceptible')) +
    geom_point() +
    xlab(row$explanatory) +
    ylab('percent susceptible') +
    theme_minimal()

@@

```{r display_results}
res %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug, resistance_drug,
         state_coherent, explanatory, correlation, p.value,
         plot_link) %>%
  kable
```

>>>>

  p = plot_dat %>%
    filter(bug==row$bug, consumption_drug==row$consumption_drug) %>%
    ggplot(aes_string(row$explanatory, 'percent_susceptible')) +
    geom_point(shape=1) +
    xlab(row$explanatory) +
    ylab('percent susceptible') +
    theme_minimal()

@@

The column `state_coherent` means that the variance in susceptibilities of the bug to the resistance drug reported in antibiograms was significantly improved by dividing the antibiogram records into states. The column `explanatory` is the explanatory variable in the Spearman correlation: either claims per 1,000 people or DID (days of drug per 1,000 people per day).

```{r display_results, echo=FALSE}
res %>%
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug, resistance_drug,
         state_coherent, explanatory, correlation, p.value,
         plot_link) %>%
  kable
```
